DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-29 paper/main.tex
Minor change to paper
Update keywords
Add Minje's part

\usepackage{microtype}%if unwanted, comment out or use option "draft"
\usepackage{adjustbox}

@@

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{Michael G. Bechtel}
\author[2]{Elise McEllhiney}
\author[3]{Heechul Yun}
\affil[1]{University of Kansas, Lawrence, United States\\
  \texttt{m783b224@ku.edu}}
\affil[2]{University of Kansas, Lawrence, United States\\
  \texttt{e908m429@ku.edu}}
\affil[3]{University of Kansas, Lawrence, United States\\
  \texttt{heechul.yun@ku.edu}}
\authorrunning{M.\,G. Bechtel, E. McEllhiney, H. Yun} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

@@

\subjclass{C.4 PERFORMANCE OF SYSTEMS}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Self-driving car, CNN, Raspberry Pi 3}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%-------------------------------------------------------------------------
\input{intro}
\input{background}
\input{overview}
\input{evaluation}
\input{comparison}
% \input{related}
\input{conclusion}
%-------------------------------------------------------------------------
%\bibliographystyle{abbrv}
\bibliography{reference}

>>>>

\usepackage{microtype}%if unwanted, comment out or use option "draft"
\usepackage{adjustbox}
\usepackage{color}
\def\fixme#1{\typeout{FIXED in page \thepage : {#1}}
%  \bgroup \color{red}{} \egroup}
\bgroup \color{red}{[FIXME: {#1}]} \egroup}

@@

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{Michael G. Bechtel}
\author[2]{Elise McEllhiney}
\author[3]{Minje Kim}
\author[4]{Heechul Yun}
\affil[1]{University of Kansas, Lawrence, United States\\
  \texttt{mbechtel@ku.edu}}
\affil[2]{University of Kansas, Lawrence, United States\\
  \texttt{e908m429@ku.edu}}
\affil[3]{Indiana University, Bloomington, United States\\
  \texttt{e908m429@ku.edu}}
\affil[4]{University of Kansas, Lawrence, United States\\
  \texttt{heechul.yun@ku.edu}}
\authorrunning{M.\,G. Bechtel, E. McEllhiney, H. Yun} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

@@

\subjclass{C.4 PERFORMANCE OF SYSTEMS}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Real-time, Autonomous car, Convolutional neural network, Case study}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%-------------------------------------------------------------------------
\input{intro}
\input{background}
\input{overview}
\input{evaluation}
\input{comparison}
\input{related}
\input{conclusion}
%-------------------------------------------------------------------------
%\bibliographystyle{abbrv}
\bibliography{reference}
